---
title: "Twitter Analysis of: `r handle`"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    theme: lumen
    css: styles.css

---

---
logo: `r logo`
data: `r data`
handle: `r handle`
collage: `r collage`
---
<style>
.navbar, [data-toggle=tab], .navbar-brand  {   background-color:white; border:2px; border-color:lightgray; color:white; }

.navbar-logo img {
    position: relative;
    right: 0px;
}
</style>

```{r}

pacman::p_load(tidyverse, glue, flexdashboard, knitr, DT, highcharter)

tl <- readRDS(data)$timeline
user <- readRDS(data)$user
links <- readRDS(data)$links

pal <- c('#2f7ed8', '#0d233a', '#8bbc21', '#910000', '#1aadce',
         '#492970', '#f28f43', '#77a1e5', '#c42525', '#a6c96a')
years <- grep("2018",sort(unique(lubridate::year(tl$created_at))), 
              invert=TRUE, value = TRUE)

```


Account Overview {data-orientation=rows}
=======================================================================

Row {data-height=500}
-----------------------------------------------------------------------

### Handle Info

```{r}
user %>% 
  select(screen_name, name, statuses_count, friends_count, followers_count, favourites_count, listed_count, description, account_created_at, user_id, profile_expanded_url, location) %>%
  mutate(account_created_at = as.character(as.Date(account_created_at)),
         across(contains("_count"), ~scales::comma(.))) %>%
  gather(Field, Value) %>%
  mutate(Field = str_to_title(str_replace_all(Field, "_", " ")),
         Field = ifelse(Field == "Profile Expanded Url", "URL", Field)) %>%
  knitr::kable(align = "lcc") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "responsive")) 
```

### Average Engagements by Year and Tweet Type 

```{r}
eng <- tl %>% 
  mutate(tweet_type = case_when(
    is_retweet ~ "Retweet",
    is_quote ~ "Quote",
    reply_to_user_id == user_id ~ "Self-Reply",
    !is.na(reply_to_user_id) ~ "Reply",
    TRUE ~ "Tweet"),
    year = lubridate::year(created_at)) %>% 
  group_by(year, tweet_type) %>% 
  summarise(fav = mean(favorite_count), rt = mean(retweet_count)) %>% 
  mutate(eng = round(fav+rt)) %>%
  select(-c(fav, rt))

highchart() %>%
  hc_add_series(eng, "column", hcaes(x = tweet_type, y = eng, group = year),
                showInLegend = TRUE) %>%
    hc_colors(pal) %>%
  hc_xAxis(type = 'category',
           title = list(text = "Tweet Type")) %>% 
  hc_yAxis(title = list(text = "Avg. Engagements")) %>% 
  hc_tooltip(crosshairs = FALSE,
             pointFormat = "<br><span style=\"color:{series.color}\">\u25CF</span> {point.year}: {point.y}<br>",
             shared = FALSE) %>%
  hc_credits(enabled = TRUE, text = "Engagements include both retweets and favorites",
             style = list(fontSize = "10px"))
```

Row {data-height=300}
-----------------------------------------------------------------------

### Daily Rhythym - Posting Cadence by Day/Hour

```{r, out.width = "100%"}
day_hour <- tl %>% 
  count(dow, hr) %>% 
  mutate(hr = sprintf("%02d:00", hr)) %>% 
  complete(dow, hr=sprintf("%02d:00", 0:23))  

hchart(day_hour, "heatmap", hcaes(x = hr, y = dow, value = n)) %>%
  hc_colorAxis(
    stops = color_stops(8, my_pal("solr"))
  ) %>%
  hc_yAxis(reversed = TRUE, 
           tickLength = 0,
           labels = list(style = list(fontSize = "10px")),
           title = list(text = "")) %>%
  hc_xAxis(title = list(text = "Hour")) %>%
  hc_plotOptions(
    series = list(list(
      stickyTracking = TRUE))) %>%
  hc_tooltip(headerFormat = "",
    pointFormat = "<b>{point.dow}</b> {point.hr} <br>
             <span style=\"color:{point.color}\">\u25CF</span> {point.n} Tweets <br>",
             shared = TRUE, style = list(pointerEvents = 'auto')) %>%
  hc_legend(layout = "vertical", verticalAlign = "top",
            align = "right", valueDecimals = 0) %>% 
  hc_credits(enabled = TRUE,
             text = "All times PST")

```

Row
-----------------------------------------------------------------------

### Daily Rhythym - Posts per Day

```{r, out.width = "100%"}
day_count <- tl %>% count(tsday) %>% 
  mutate(id = row_number())
# fit the predicted loess line
library(broom)
modlss <- loess(n ~ id, data = day_count)
fit <- augment(modlss) %>% arrange(id) %>% 
  mutate(.fitted = round(.fitted, digits = 2))

highchart() %>%
  hc_xAxis(categories = day_count$tsday) %>%
  hc_yAxis(title = list(text = "Daily Tweets"), ymin = 0) %>%
  hc_add_series(day_count, type = "column", hcaes(x = id, y = n), name = "Count") %>%
  hc_add_series(fit, type = "spline", hcaes(x = id, y = .fitted), name = "Average") %>% 
    hc_colors(pal) %>%
  hc_plotOptions(spline = list(color = pal[1],
                             marker = list(
                               fillColor = "white",
                               lineWidth = 2,
                               lineColor = NULL,
                               radius = 0
                               ))) 
```

### Posts by Day of Week 

```{r}
dow_ct <- count(tl, dow) %>% 
  mutate(frac = n/sum(n),
         frac = scales::percent(frac, accuracy = 1))

highchart() %>%
  hc_add_series(dow_ct, "column", hcaes(x = dow, y = n), color = pal[1],
                showInLegend = FALSE) %>%
  hc_xAxis(categories = dow_ct$dow) %>% 
  hc_yAxis(title = list(text = "Total Tweets")) %>% 
  hc_tooltip(headerFormat = "",
    pointFormat = "<b>{point.dow}</b><br>
             <span style=\"color:{point.color}\">\u25CF</span> {point.n} Tweets <br>
             <span style=\"color:{point.color}\">\u25CF</span> {point.frac} of Total<br>",
             shared = TRUE, style = list(pointerEvents = 'auto'))
```

Row
-----------------------------------------------------------------------

### Tweet Type 

```{r}
tweet_type <- mutate(tl, tweet_type = case_when(
  is_retweet ~ "Retweet",
  is_quote ~ "Quote",
  reply_to_user_id == user_id ~ "Self-Reply",
  !is.na(reply_to_user_id) ~ "Reply",
  TRUE ~ "Tweet"
)) %>% 
  count(tweet_type, sort=TRUE) %>% 
  mutate(frac = scales::percent(n/sum(n), accuracy = 1))

hcoptslang <- getOption("highcharter.lang")
hcoptslang$thousandsSep <- ","
options(highcharter.lang = hcoptslang)

highchart() %>%
  hc_add_series(tweet_type, "bar", hcaes(x = tweet_type, y = n), color = pal[1],
                showInLegend = FALSE) %>% 
  hc_xAxis(categories = tweet_type$tweet_type) %>% 
  hc_tooltip(crosshairs = TRUE,
             headerFormat = "",
             pointFormat = "<b>{point.tweet_type}</b><br>
                            <span style=\"color:{point.color}\">\u25CF</span> Tweets: {point.y}<br>
                          <span style=\"color:{point.color}\">\u25CF</span> % of Tweets {point.frac}<br>") %>%
  hc_plotOptions(line = list(
                             marker = list(
                               enabled = FALSE
                               )))
```

### Used Interface

```{r}
ui <- count(tl, source, sort=TRUE) %>% 
  mutate(source = fct_inorder(source) %>% fct_rev(),
         frac = scales::percent(n/sum(n), accuracy = 1))

highchart() %>%
  hc_add_series(ui, "bar", hcaes(x = source, y = n), color = pal[1],
                showInLegend = FALSE) %>% 
  hc_xAxis(categories = ui$source) %>% 
  hc_tooltip(crosshairs = TRUE,
             headerFormat = "",
             pointFormat = "<b>{point.source}</b><br>
                            <span style=\"color:{point.color}\">\u25CF</span> Tweets: {point.y}<br>
                          <span style=\"color:{point.color}\">\u25CF</span> % of Tweets {point.frac}<br>")

```

Row
-----------------------------------------------------------------------

### Hashtag Usage

```{r}
hash <- unlist(tl$hashtags) %>% 
  discard(is.na) %>% 
  # tolower() %>% 
  fct_lump(n = 15, ties = "first") %>% 
  table(dnn="hashtag") %>%
  as_tibble() %>%
  # broom::tidy() %>% 
  arrange(desc(n)) %>% 
  mutate(hashtag = factor(hashtag, levels = c(setdiff(hashtag, "Other"), "Other")) %>% fct_rev())

highchart() %>%
  hc_add_series(hash, "bar", hcaes(x = hashtag, y = n), color = pal[1],
                showInLegend = FALSE) %>% 
  hc_xAxis(categories = hash$hashtag) %>% 
  hc_tooltip(crosshairs = TRUE,
             headerFormat = "",
             pointFormat = "<b>#{point.hashtag}</b><br>
                            <span style=\"color:{point.color}\">\u25CF</span> Count: {point.y}<br>")
```

### Links Shared 

```{r, error = TRUE}
top_url <- links %>%
  pull() %>% 
  urltools::domain() %>% 
  urltools::suffix_extract() %>% 
  as_tibble() %>% 
  mutate(apex = glue::glue("{domain}.{suffix}")) %>% 
  mutate(apex = fct_lump(apex, n = 10, ties = "first")) %>% 
  count(apex, sort=TRUE) %>% 
  mutate(apex = factor(apex, levels = c(setdiff(apex, "Other"), "Other"))) %>% 
  filter(apex != "Other")

highchart() %>%
  hc_add_series(top_url, "bar", hcaes(x = apex, y = n), color = pal[1],
                showInLegend = FALSE) %>% 
  hc_xAxis(categories = top_url$apex) %>% 
  hc_tooltip(crosshairs = TRUE,
             headerFormat = "",
             pointFormat = "<b>#{point.apex}</b><br>
                            <span style=\"color:{point.color}\">\u25CF</span> Count: {point.y}<br>")
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Replied Users 

```{r}
reply <- unlist(tl$reply_to_screen_name) %>% 
  discard(is.na) %>% 
  tolower() %>% 
  fct_lump(n = 10, ties = "first") %>% 
  table(dnn="replied_to_users") %>% 
  as_tibble() %>%
  # broom::tidy() %>% 
  arrange(desc(n)) %>% 
  mutate(replied_to_users = factor(replied_to_users, levels = c(setdiff(replied_to_users, "Other"), "Other")) %>% fct_rev()) %>% 
  filter(replied_to_users != "Other")

highchart() %>%
  hc_add_series(reply, "bar", hcaes(x = replied_to_users, y = n), color = pal[1],
                showInLegend = FALSE) %>% 
  hc_xAxis(categories = reply$replied_to_users) %>% 
  hc_tooltip(crosshairs = TRUE,
             headerFormat = "",
             pointFormat = "<b>#{point.replied_to_users}</b><br>
                            <span style=\"color:{point.color}\">\u25CF</span> Count: {point.y}<br>")
```

### Retweeted Users 

```{r}
retweet <- unlist(tl$retweet_screen_name) %>% 
  discard(is.na) %>% 
  tolower() %>% 
  fct_lump(n = 10, ties = "first") %>% 
  table(dnn="retweeted_users") %>% 
  as_tibble() %>%
  # broom::tidy() %>% 
  arrange(desc(n)) %>% 
  mutate(retweeted_users = factor(retweeted_users, levels = c(setdiff(retweeted_users, "Other"), "Other")) %>% fct_rev())

highchart() %>%
  hc_add_series(retweet, "bar", hcaes(x = retweeted_users, y = n), color = pal[1],
                showInLegend = FALSE) %>% 
  hc_xAxis(categories = retweet$retweeted_users,
           allowDecimals = FALSE) %>% 
  hc_yAxis(allowDecimals = FALSE) %>%
  hc_tooltip(crosshairs = TRUE,
             headerFormat = "",
             pointFormat = "<b>#{point.retweeted_users}</b><br>
                            <span style=\"color:{point.color}\">\u25CF</span> Count: {point.y}<br>")
```

### Quoted Users 

```{r}
quote <- unlist(tl$quoted_screen_name) %>% 
  discard(is.na) %>% 
  tolower() %>% 
  fct_lump(n = 10, ties = "first") %>% 
  table(dnn="quoted_users") %>% 
  as_tibble() %>%
  # broom::tidy() %>% 
  arrange(desc(n)) %>% 
  mutate(quoted_users = factor(quoted_users, levels = c(setdiff(quoted_users, "Other"), "Other")) %>% fct_rev())

highchart() %>%
  hc_add_series(quote, "bar", hcaes(x = quoted_users, y = n), color = pal[1],
                showInLegend = FALSE) %>% 
  hc_xAxis(categories = quote$quoted_users) %>%
  hc_yAxis(allowDecimals = FALSE) %>%
  hc_tooltip(crosshairs = TRUE,
             headerFormat = "",
             pointFormat = "<b>#{point.quoted_users}</b><br>
                            <span style=\"color:{point.color}\">\u25CF</span> Count: {point.y}<br>")

```

Tweets 
=======================================================================

Row 
-----------------------------------------------------------------------

### Tweets 

```{r}

mutate(tl, tweet_type = case_when(
  is_retweet ~ "Retweet",
  is_quote ~ "Quote",
  reply_to_user_id == user_id ~ "Self-Reply",
  !is.na(reply_to_user_id) ~ "Reply",
  TRUE ~ "Tweet"),
  link = "Link",
  link = paste0('<a href="',status_url,'"target="_blank">',link ,"</a>"),
  created_at = as.Date(created_at)
) %>%
  select(created_at, tweet_type, text, retweet_count, favorite_count, link, status_url) %>%
  DT::datatable(fillContainer = FALSE, escape = -6, filter = 'top',
                extensions = "Buttons", rownames = FALSE,
                options = list(dom = "Blfrtip",
                               buttons = c('csv', 'excel'),
                               pageLength = 20,
                               columnDefs = list(list(width = '350px', targets = 2),
                                                 list(visible=FALSE, targets = c(6)))))

```

Media Imagery {data-orientation=rows}
=======================================================================

Row {.tabset data-height=1100}
-----------------------------------------------------------------------

### Imagery Used - `r years[1]`  

<!-- Div fencing (https://bookdown.org/yihui/rmarkdown-cookbook/multi-column.html) -->
:::: {style="display: flex;"}

```{r, error = TRUE, fig.retina = 1}
knitr::include_graphics(collages[1])
```

:::: 

### Imagery Used - `r years[2]`  

:::: {style="display: flex;"}

```{r, error = TRUE, fig.retina = 1}
knitr::include_graphics(collages[2])
```

:::: 


### Imagery Used - `r years[3]`  

:::: {style="display: flex;"}

```{r, error = TRUE, fig.retina = 1}
knitr::include_graphics(collages[3])
```

:::: 

